---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# redcapdd


[![Travis-CI Build Status](https://travis-ci.org/Sage-Bionetworks/redcapdd.svg?branch=master)](https://travis-ci.org/Sage-Bionetworks/redcapdd)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

The goal of redcapdd is to generate properly formatted data dictionaries for
upload to REDCap.

## Installation

```{r, eval = FALSE} 
devtools::install_github("Sage-Bionetworks/redcapdd")
```

## Creating data dictionaries

You can create a new field with `create_fields()`. The result will have all of
the columns required in a REDCap data dictionary.

When called with no arguments, `create_fields()` provides a one-row data frame
containing all NAs.

```{r create_fields}
library("redcapdd")
create_fields()
```

You can provide as much information as you want to populate the field;
`create_fields()` will fill out the rest of the columns with NAs.

```{r create_fields_2}
x <- list(
  `Variable / Field Name` = "patient_name",
  `Field Label` = "Patient name",
  `Identifier?` = "y"
)

create_fields(x)
```

There are a number of aliases to `create_fields()` that support the creation of
specific field types. These include `create_checkbox_field()`,
`create_text_field()`, and others. See `?create_fields` for more information.

redcapdd also supports chaining operations with `%>%` and the `add_field()`
function. Like `create_fields()`, `add_field()` has aliases for different field
types.

```{r add_field}
create_dd_template() %>%
  add_text_field(
    `Variable / Field Name` = "patient_name",
    `Field Label` = "Patient name",
    `Identifier?` = "y"
  ) %>%
  add_truefalse_field(
    `Variable / Field Name` = "given_birth",
    `Field Label` = "Patient has given birth?"
  )
```

## Other functionality

Certain field types such as dropdown, radio, and checkbox can take multiple
options in the `Choices, Calculations, OR Slider Labels` column. These options
need to be in a specific format to be accepted by REDCap's data dictionary
validator: `1, option1 | 2, option2` and so on. You can create a string in this
format from a character vector with the `create_choices()` function.

```{r create_choices}
x <- c("red", "green", "blue")
create_choices(x)
```

## Exporting your data dictionary

`write_dd()` will export your data dictionary with the correct fields quoted.
Some must be quoted, but others cannot be or the REDCap validator will complain
that the empty strings are invalid values; `write_dd()` takes care of this for
you.

```{r write_dd, eval = FALSE}
dd <- create_fields(x)
write_dd(dd, "data_dictionary.csv")
```
