---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# redcapdd


[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

The goal of redcapdd is to generate properly formatted data dictionaries for
upload to REDCap.

## Installation

```{r, eval = FALSE} 
devtools::install_github("Sage-Bionetworks/redcapdd")
```

## Examples

You can create a new field with `create_fields()`. The result will have all of
the columns required in a REDCap data dictionary.

When called with no arguments, `create_fields()` provides a one-row data frame
containing all NAs.

```{r create_fields}
library("redcapdd")
create_fields()
```

You can provide as much information as you want to populate the field;
`create_fields()` will fill out the rest of the columns with NAs.

```{r create_fields_2}
x <- list(
  `Variable / Field Name` = "patient_name",
  `Field Label` = "Patient name"
)

create_fields(x)
```
